On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-03 paper.tex
Rewrote the Chichen Itza part
The previous version was hard to follow, because one got lost in the details. I think now it is much more readable and looks more organized.

The only modification to the main file, paper.tex are some package declarations.
Forgot to uncomment the includes I commented before for faster compilation
Binding capability
The definition of bc was not correct so that I fixed it.
Lenght of conformation defined
As stated in the title.

\usepackage{graphicx}
\usepackage{tikz}
\usepackage{calc}

@@

@@

%Results
\node at (1, 4) {$O(n^2)$};
\node at (1, 3) {$O(n)$};
\node at (1, 2) {$O(n^2)$};
\node at (1, 1) {$O(n)$ \cite{DemaineDNA24}};

@@

Oritatami systems fold their transcript, which is a sequence of beads, over the triangular grid graph $\mathbb{T} = (V, E)$ cotranscriptionally. 
We designate one point in $V$ as the origin $O$ of $\mathbb{T}$. 
For a point $p \in V$, let $N_p^d$ denote the set of points which lie in the regular hexagon of radius $d$ centered at the point $p$. 
A directed path $P = p_1 p_2 \cdots p_n$ in $\mathbb{T}$ is a sequence of \textit{pairwise-distinct} points $p_1, p_2, \ldots, p_n \in V$ such that $\{p_i, p_{i+1}\} \in E$ for all $1 \le i < n$. 
Its $i$-th point is referred to as $P[i]$. 
Now we are ready to abstract RNA single-stranded structures in the name of conformation. 
A \textit{conformation} $C$ (over $\Sigma$) is a triple $(P, w, H)$ of a directed path $P$ in $\mathbb{T}$, $w \in \Sigma^*$ of the same length as $P$, and a set of h-interactions $H \subseteq \bigl\{\{i, j\} \bigm| 1 \le i, i+2 \le j, \{P[i], P[j]\} \in E \bigr\}$. 
This is to be interpreted as the sequence $w$ being folded along the path $P$ in such a manner that its $i$-th bead $w[i]$ is placed at the $i$-th point $P[i]$ and the $i$-th and $j$-th beads are bound (by a hydrogen-bond-based interaction) if and only if $\{i, j\} \in H$. 
The condition $i+2 \le j$ represents the topological restriction that two consecutive beads along the path cannot be bound. 
A \textit{rule set} $R \subseteq \Sigma \times \Sigma$ is a symmetric relation over $\Sigma$, that is, for all bead types $a, b \in \Sigma$, $(a, b) \in R$ implies $(b, a) \in R$. 
A bond $\{i, j\} \in H$ is \textit{valid with respect to $R$}, or simply $R$-valid, if $(w[i], w[j]) \in R$. 
This conformation $C$ is \textit{$R$-valid} if all of its bonds are $R$-valid. 
For an integer $\alpha \ge 1$, $C$ is \textit{of arity $\alpha$} if it contains a bead that forms $\alpha$ bonds but none of its bead forms more. 
By $\mathcal{C}_{\le \alpha}(\Sigma)$, we denote the set of all conformations over $\Sigma$ whose arity is at most $\alpha$; its argument $\Sigma$ is omitted whenever $\Sigma$ is clear from the context.

@@

In the second half of this paper, we consider the unary oritatami system. 
An oritatami system is \textit{unary} if its bead type set $\Sigma$ is of size 1. 
Its sole bead type is denoted by $a$, that is, $\Sigma = \{a\}$. 
Its only possible rule is $(a, a)$ so that the non-empty rule set assumption implies that its rule set is $R = \{(a, a)\}$. 
Its transcript is a sequence of $a$-beads. 
That is to say, the behavior of a unary oritatami system is fully determined by the delay, arity, and seed.

@@

\bibliographystyle{splncs03}
\bibliography{tamc2019.bib}

>>>>

\usepackage{graphicx}
\usepackage{tikz}
\usepackage{calc}
\usepackage{array}

@@

\usepackage{comment}

@@

%Results
\node at (1, 4) {$O(n^2)$};
\node at (1, 3) {$O(n)$};
\node at (1, 2) {$O(n^2)$};
\node at (1, 1) {$9n$ \cite{DHOPRSST2018}};

@@

Oritatami systems fold their transcript, which is a sequence of beads, over the triangular grid graph $\mathbb{T} = (V, E)$ cotranscriptionally. 
We designate one point in $V$ as the origin $O$ of $\mathbb{T}$. 
For a point $p \in V$, let $\hexagon_p^d$ denote the set of points which lie in the regular hexagon of radius $d$ centered at the point $p$. 
Note that $\hexagon_p^d$ consists of $3d(d+1)+1$ points. 
A directed path $P = p_1 p_2 \cdots p_n$ in $\mathbb{T}$ is a sequence of \textit{pairwise-distinct} points $p_1, p_2, \ldots, p_n \in V$ such that $\{p_i, p_{i+1}\} \in E$ for all $1 \le i < n$. 
Its $i$-th point is referred to as $P[i]$. 
Now we are ready to abstract RNA single-stranded structures in the name of conformation. 
A \textit{conformation} $C$ (over $\Sigma$) is a triple $(P, w, H)$ of a directed path $P$ in $\mathbb{T}$, $w \in \Sigma^*$ of the same length as $P$, and a set of h-interactions $H \subseteq \bigl\{\{i, j\} \bigm| 1 \le i, i+2 \le j, \{P[i], P[j]\} \in E \bigr\}$. 
This is to be interpreted as the sequence $w$ being folded along the path $P$ in such a manner that its $i$-th bead $w[i]$ is placed at the $i$-th point $P[i]$ and the $i$-th and $j$-th beads are bound (by a hydrogen-bond-based interaction) if and only if $\{i, j\} \in H$. 
The condition $i+2 \le j$ represents the topological restriction that two consecutive beads along the path cannot be bound. 
The \textit{length} of $C$ is defined to be the length of its transcript $w$ (that is, equal to the length of the path $P$). 
A \textit{rule set} $R \subseteq \Sigma \times \Sigma$ is a symmetric relation over $\Sigma$, that is, for all bead types $a, b \in \Sigma$, $(a, b) \in R$ implies $(b, a) \in R$. 
A bond $\{i, j\} \in H$ is \textit{valid with respect to $R$}, or simply $R$-valid, if $(w[i], w[j]) \in R$. 
This conformation $C$ is \textit{$R$-valid} if all of its bonds are $R$-valid. 
For an integer $\alpha \ge 1$, $C$ is \textit{of arity $\alpha$} if it contains a bead that forms $\alpha$ bonds but none of its bead forms more. 
By $\mathcal{C}_{\le \alpha}(\Sigma)$, we denote the set of all conformations over $\Sigma$ whose arity is at most $\alpha$; its argument $\Sigma$ is omitted whenever $\Sigma$ is clear from the context.

@@

In this paper, we considerably focus on the unary oritatami system. 
An oritatami system is \textit{unary} if its bead type set $\Sigma$ is of size 1. 
Its sole bead type is denoted by $a$, that is, $\Sigma = \{a\}$. 
Its only possible rule is $(a, a)$ so that the non-empty rule set assumption implies that its rule set is $R = \{(a, a)\}$. 
Its transcript is a sequence of $a$-beads. 
That is to say, the behavior of a unary oritatami system is fully determined by the delay, arity, and seed.

@@

\bibliographystyle{splncs03}
\bibliography{tamc2019}
